On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-07 MS.tex
Clean code: change name fig

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database. Green and red lines are the cutoffs between stage categories used in the literature. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{fig:figA1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
\label{fig:figA2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Results shown here are from the ``complete'' dataset (recorded both across and within species
and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and green
points to juveniles.}
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). On panels B, relative (RGR) and absolute (AbsGR) growth rates are set appart. The mean coefficients are weighted by sample size and established from 112 articles and. Results shown here are from the ''ideal dataset''.  ''n'' indicate the number of correlation.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data (under unstressed conditions), grey points: all the data. ``n'' indicate the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). n = number of correlation r reported. Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA). AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Results shown here are from ``ideal'' dataset (recorded at interspecific and under unstressed condition) and ``complete'' dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)}. Results shown here are from the ``ideal'' dataset (recorded across species and under unstressed conditions).  Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation. The number of species is sometimes as low as 1, and these are within-species correlations. The number of replicates used for the correlation coefficient was often much greater than the number of species. Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high. The open points correspond to the estimated missing studies. The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea}
\label{fig:figA7}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} Results shown here are from the ``complete'' dataset (recorded under both unstressed and stressed conditions). On the right side of each graph are the Absolute growth rates (AbsGR), on the left side the relative growth rate (RGR).}
\label{fig:figA8}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
\caption{\textbf{Temporal changes in coefficient of correlation between traits and growth. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)} Results shown here are from the ``ideal'' dataset (recorded across species and under  unstressed conditions). The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
\label{fig:figA9}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
\caption{\textbf{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.} Green and red lines are the cutoffs between stage categories used in the literature. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{fig:figA1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis}. Results shown here are from the ``complete'' dataset (see methods for details).}
\label{fig:figA2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{\textbf{Range of correlations (r) between
growth and trait reported in the literature (112 articles)}. Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Results shown here are from the ``complete'' dataset (see methods for details). Each bubble represents a r value, the diameter of the bubble is proportional to its weights in the meta-analysis (i.e. number of species used). The colors correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and green
points to juveniles.}
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth and traits.} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).  On panels B, relative (RGR) and absolute (AbsGR) growth rates are set appart. The mean coefficients are weighted by sample size and established from 112 articles and. Results shown here are from the ''ideal dataset'' (see methods for details).  ''n'' indicate the number of correlation.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study}. Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data , grey points: all the data (see methods for details). ''n'' indicate the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). n = number of correlation r reported. Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA). AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Results shown here are from ``ideal'' dataset (see methods for details).}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{\textbf{Funnel plots with filled in data based on the trim and fill method}, showing transformed correlation coefficient z between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Results shown here are from the ''ideal'' dataset (see material and methode for details).  Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation. The number of species is sometimes as low as 1, and these are within-species correlations. The number of replicates used for the correlation coefficient was often much greater than the number of species. Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high. The open points correspond to the estimated missing studies. The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea.}
\label{fig:figA7}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). On the right side of each graph are the absolute growth rates (AbsGR), on the left side the relative growth rate (RGR). Results shown here are from the ``complete'' dataset (see methods for details). }
\label{fig:figA8}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
\caption{\textbf{Temporal changes in coefficient of correlation between growth and traits}. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Results shown here are from the ``ideal'' dataset (see methods for details). The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
\label{fig:figA9}
\end{figure}
